Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-09-06 papers/paper_review/response_1.txt

REVIEWER COMMENT
----------
The discussion of Li could use further clarity.
- Identification of which stars have Li is inconsistent. Line 456 says neither component of 7913 has strong Li, but at line 477 Li is obvious in all but one star, and at line 487 Li is noted as secure in 7913A.
- Line 497: "Lack of Li" implies there's no Li, not that there's not as much as expected
- As I mentioned previously, I am skeptical of the 1% false positive rate for RSG-5
- The authors point out an interesting possibility about why the Li in 1643 could be low, namely that the dispersion could be higher than expected. Though I am not an expert in Li, this seems reasonable. However, I think it should be qualified a bit more: how many stars were previously studied; few enough that scatter could be missed? Why might RSG-5 be different?
- Did the authors consider initial Li abundance, or differences in Fe abundance, as a possible reason for differences in current Li? 1643 certainly stands out the most, but I might be able to argue from Fig 4 that on average, the observed planet hosts in Cep-Her are all a bit lower than expected from the reference sequences.

RESPONSE
----------
> - The wording at L456 has been updated as follows: "The primary showed lithium in absorption with ${\rm EW}_{\rm Li} = 65^{+8}_{-6}$\,m\AA, while the secondary had a marginal detection of ${\rm EW}_{\rm Li} = 42^{+12}_{-19}$\,m\AA."
>
> - The wording at L497 has similary been adjusted.
>
> - Regarding the 1% false postive rate, we have previously addressed that photometrically, 88/89= 98.9% of the candidate RSG-5 members redward of (BP-RP)0=1.5 are consistent with being on the pre-main-sequence.  Based on rotation periods, the relevant fraction was 39/42 (93%).  The detection process for stellar rotation periods is more complicated than that for measuring a star's brightness and color, so our initial wording of "$\approx 1\%$ false positive probability" seems accurate.  We have nonetheless replaced the text with the term "few-percent false positive probability".  This does not change the conclusion, which is based on both the FPP from the spatio-kinematic selection, as well as the chance of selecting an interloping field star at this color with a sub-Pleiades rotation period.
>
> - We have added a sentence quantifying the discrepancy: "Quantitatively, there are 14 reference stars within $\pm$150\,K of Kepler-1643.  The mean and standard deviation of their lithium EWs is $255 \pm 31$\,m\AA, which implies that Kepler-1643 is $4.0$-$\sigma$ discrepant from expectations."  We have also added sentences indicating that given these ~dozen stars, an anomalous Li EW scatter would indeed be surprising.  However, in our view it remains the most plausible interpretation.  The suggested alternative of differences in overall metallicity seems unlikely because the [Fe/H] abundances measured for the Kepler Objects of Interest are all near-solar.
>
> - In constructing this response, a typo was correct: the manuscript previously referenced Randich+2018 for the lithium sample in IC-2602.  The correct reference is Randich+2001.  We did consider the Randich+2018 study, but the results were qualitatively the same, but with less clearly stated uncertainties on the equivalent width measurements, and a selection function (their Figure 1b) that we did not want to impose.

### 2022-09-06 papers/paper/ms.tex
update response

\paragraph{Spectra}
We acquired Keck/HIRES spectra for KOI-7913 A on the night of 2021 Nov
13, and KOI-7913 B on the night of 2021 Oct 26.  The
\texttt{SpecMatch-Emp} machinery yielded $T_{\rm eff,A} = 4324 \pm
70\,{\rm K}$, and $T_{\rm eff,B} = 4038 \pm 70\,{\rm K}$.  \replaced{The
remaining parameters were in agreement}{These temperatures as well as the other spectroscopic parameters agreed} with those from the cluster
isochrone\added{ method within 1-$\sigma$}.  For the primary, we also found $[{\rm Fe/H}]= -0.06 \pm
0.09$, $v\sin i = 13.3 \pm 1.0\,\mkms$, and ${\rm RV}_{\rm sys} =
-17.8 \pm 1.1\,\mkms$.  For the secondary, these same parameters were
$[{\rm Fe/H}]= -0.01 \pm 0.09$, $v\sin i = 10.7 \pm 1.0\,\mkms$, and
${\rm RV}_{\rm sys} = -18.8 \pm 1.1\,\mkms$.  Neither of the KOI-7913
components shows strong lithium absorption, but this is expected given
their $\approx$K6V and $\approx$K8V spectral types.  They do however
both show H$\alpha$ in emission.  Broadly speaking, both observations
are consistent with a $\approx$40 Myr age for KOI-7913 (see
Section~\ref{subsec:specyouth}).

@@

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f6c.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Lithium 6708\AA\ and H$\alpha$ equivalent widths for the
    objects of interest compared to young open clusters and field
    stars. } Positive equivalent width means absorption; negative
    equivalent width means emission.  
    {\it Top \& middle}:
    The field stars are KOIs from
    \citet{berger_identifying_2018}.  The ``40-50 Myr'' reference
    stars ({\it left}) are from IC\,2602 \citep{randich_gaiaeso_2018} and
    Tuc-Hor \citep{kraus_stellar_2014}.  The ``112 Myr'' stars
    are from the Pleiades
    \citep{soderblom_evolution_1993,jones_evolution_1996,bouvier_pleiades_lirot_2018}.
    The statistical uncertainties on
    the equivalent widths are shown, or else are
    smaller than the markers.
    {\it Bottom}:
    The H$\alpha$ comparison is against Tuc-Hor
    \citep[$\approx$$40$\,Myr;][]{kraus_stellar_2014}
    \label{fig:lithium}
	}
\end{figure}

@@

Kepler-1643, in RSG-5, is conspicuously below the 40-50$\,$Myr
sequence in the left-panel of Figure~\ref{fig:lithium}, though
above the field stars (${\rm EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA).
The right panel shows the comparison against the Pleiades, where
Kepler-1643 is more consistent with the observed dispersion in
lithium.

One explanation for the lack of Li in Kepler-1643 could be that it is a field
interloper; another could be that RSG-5 is much older than 50\,Myr.  We do
not favor either explanation.  
RSG-5 cannot be much older than 50\,Myr
based on its proximity to the $\delta$~Lyr cluster and IC\,2602 in the
CAMD, and because it is below the Pleiades in the 
rotation versus color diagram (Figure~\ref{fig:age}).
Kepler-1643 also seems highly unlikely to be a field interloper, 
because we demonstrated a $\approx$$1\%$ false positive probability
in our spatio-kinematic selection of RSG-5 members, and there is a 
similar independent chance
($\approx$$1\%$) of a field K2V star having a rotation period below the
Pleiades \citep{mcquillan_rotation_2014}.
This yields a puzzle: how could a star have spatial, kinematic, and rotational
evidence consistent with being in a $\approx$50\,Myr cluster,
but a low lithium content?

Our preferred explanation for Kepler-1643's meager lithium 
content is that the reference sample of IC\,2602 and Tuc-Hor
stars may not fully explore all possible stellar rotation
periods and lithium equivalent widths at this age. 
Considering the top panels of Figure~\ref{fig:lithium}, it is remarkable that in
50 million years, stars between $4500$\,K and $5200$\,K go from
having a tight lithium sequence to one with a dispersion
$\approx10\times$ greater.  The existence of the Li dispersion in
Pleiades-age K-dwarfs has been known for decades; it has also been
known that the stars with the largest lithium abundances are also the
most rapidly rotating
\citep{butler_pleiades_1987,soderblom_evolution_1993}.  More recent
analyses of this correlation have been reviewed by
\citet{bouvier_lithium-rotation_2020}.  The conclusion of that work
was that the origin of the rotation-lithium correlation likely lies
within pre-main-sequence stellar physics.  If so, one would expect the
IC\,2602 and Tuc-Hor K-dwarfs to show a larger intrinsic lithium
dispersion.  A recent analysis of the $\approx$40\,Myr
NGC~2547 by \citet{binks_2022} suggests that this may
be the case, though that study only had $\approx$10 stars in the relevant
effective temperature range.
This suggests that
RSG-5 and Cep-Her could be
worthy objects for a closer analysis of the lithium-rotation correlation
near the zero-age main sequence.

>>>>

\paragraph{Spectra}
We acquired Keck/HIRES spectra for KOI-7913 A on the night of 2021 Nov
13, and KOI-7913 B on the night of 2021 Oct 26.  The
\texttt{SpecMatch-Emp} machinery yielded $T_{\rm eff,A} = 4324 \pm
70\,{\rm K}$, and $T_{\rm eff,B} = 4038 \pm 70\,{\rm K}$.  \replaced{The
remaining parameters were in agreement}{These temperatures as well as the other spectroscopic parameters agreed} with those from the cluster
isochrone\added{ method within 1-$\sigma$}.  For the primary, we also found $[{\rm Fe/H}]= -0.06 \pm
0.09$, $v\sin i = 13.3 \pm 1.0\,\mkms$, and ${\rm RV}_{\rm sys} =
-17.8 \pm 1.1\,\mkms$.  For the secondary, these same parameters were
$[{\rm Fe/H}]= -0.01 \pm 0.09$, $v\sin i = 10.7 \pm 1.0\,\mkms$, and
${\rm RV}_{\rm sys} = -18.8 \pm 1.1\,\mkms$.  \replaced{Neither of the KOI-7913
components shows strong lithium absorption, but this is expected given
their $\approx$K6V and $\approx$K8V spectral types}{The primary showed lithium in absorption
with ${\rm EW}_{\rm Li} =
65^{+8}_{-6}$\,m\AA, while the secondary had a marginal detection of ${\rm EW}_{\rm Li} =
42^{+12}_{-19}$\,m\AA. }.  \replaced{They do however
both show H$\alpha$ in emission.  Broadly speaking, both}{Both components displayed 
H$\alpha$ in emission.  Given the spectral types of the stars, these} observations
are consistent with a $\approx$40 Myr age for KOI-7913 (see
Section~\ref{subsec:specyouth}).

@@

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f6c.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Lithium 6708\AA\ and H$\alpha$ equivalent widths for the
    objects of interest compared to young open clusters and field
    stars. } Positive equivalent width means absorption; negative
    equivalent width means emission.  
    {\it Top \& middle}:
    The field stars are KOIs from
    \citet{berger_identifying_2018}.  The ``40-50 Myr'' reference
    stars ({\it left}) are from IC\,2602 \replaced{\citep{randich_gaiaeso_2018}}{\citep{randich_2001}} and
    Tuc-Hor \citep{kraus_stellar_2014}.  The ``112 Myr'' stars
    are from the Pleiades
    \citep{soderblom_evolution_1993,jones_evolution_1996,bouvier_pleiades_lirot_2018}.
    The statistical uncertainties on
    the equivalent widths are shown, or else are
    smaller than the markers.
    {\it Bottom}:
    The H$\alpha$ comparison is against Tuc-Hor
    \citep[$\approx$$40$\,Myr;][]{kraus_stellar_2014}
    \label{fig:lithium}
	}
\end{figure}

@@

Kepler-1643, in RSG-5, is conspicuously below the 40-50$\,$Myr
sequence in the left-panel of Figure~\ref{fig:lithium}, though
above the field stars (${\rm EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA).
added{
Quantitatively, there are 14 reference stars within $\pm$150\,K of Kepler-1643.
The mean and standard deviation of their lithium EWs is $255 \pm 31$\,m\AA,
which implies that Kepler-1643 is $4.0$-$\sigma$ discrepant from expectations.
}
The right panel shows the comparison against the Pleiades, where
Kepler-1643 is more consistent with the observed dispersion in
lithium.

One explanation for the \replaced{lack of Li in Kepler-1643}{low Li equivalent width
in Kepler-1643 relative to the comparison stars} could be that it is a field
interloper; another could be that RSG-5 is much older than 50\,Myr.  We do
not favor either explanation.  
RSG-5 cannot be much older than 50\,Myr
based on its proximity to the $\delta$~Lyr cluster and IC\,2602 in the
CAMD, and because it is below the Pleiades in the 
rotation versus color diagram (Figure~\ref{fig:age}).
Kepler-1643 also seems highly unlikely to be a field interloper, 
because we demonstrated a \replaced{$\approx$$1\%$}{few-percent} false positive probability
in our spatio-kinematic selection of RSG-5 members, and there is a 
similar independent chance
($\approx$$1\%$) of a field K2V star having a rotation period below the
Pleiades \citep{mcquillan_rotation_2014}.
This yields a puzzle: how could a star have spatial, kinematic, and rotational
evidence consistent with being in a $\approx$50\,Myr cluster,
but a low lithium content?

Our preferred explanation for Kepler-1643's meager lithium 
content is that the reference sample\added{s} of IC\,2602 and Tuc-Hor
stars may not fully explore all possible stellar rotation
periods and lithium equivalent widths at this age.
\added{This would be somewhat surprising since over a dozen
stars have already been analyzed in the relevant effective temperature range. However, considering}
the top panels of Figure~\ref{fig:lithium}, it is remarkable that in
50 million years, stars between $4500$\,K and $5200$\,K go from
having a tight lithium sequence to one with a dispersion
$\approx10\times$ greater.  The existence of the Li dispersion in
Pleiades-age K-dwarfs has been known for decades; it has also been
known that the stars with the largest lithium abundances are also the
most rapidly rotating
\citep{butler_pleiades_1987,soderblom_evolution_1993}.  More recent
analyses of this correlation have been reviewed by
\citet{bouvier_lithium-rotation_2020}.  The conclusion of that work
was that the origin of the rotation-lithium correlation likely lies
within pre-main-sequence stellar physics.  If so, one would expect the
IC\,2602 and Tuc-Hor K-dwarfs to show a larger intrinsic lithium
dispersion.  A recent analysis of the $\approx$40\,Myr
NGC~2547 by \citet{binks_2022} suggests that this may
be the case, though that study only had $\approx$10 stars in the relevant
effective temperature range.
\added{An alternative explanation could be that the overall metallicity of the cluster 
is different from Tuc-Hor and IC\,2602, but this seems unlikely given the near-solar
metallicities we have measured for the Kepler Objects of Interest.}
\replaced{This suggests}{Broadly, these considerations suggest} that
RSG-5 and Cep-Her could be
worthy objects for a \replaced{closer analysis of the lithium-rotation correlation}{spectroscopic analysis of lithium}
near the zero-age main sequence.
